### 2018-03-22 morus.tex
linear approximation fragments

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{subfigure}{.3\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (C) -- node[below] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (xnd-1) -- (and-1) (xor-1) -- (txor-1) (txor-1) -- (tanB0) (tanB0) -- (tanB0-|and0.east)
      (and0) -- (xnd0) (xnd0) -- (tlll-1) (xnd0) -- (xor0)
      (and-1.east|-tanA-1) -- (tanA-1) (tanA-1) -- (txor0) (txor0) -- (xor0)
      (xor0) -- (lll0) (lll0) -- (W40) node[below] {$i+5$}
      (W-20) node[above] {\phantom{$i$}}
      ;
  \end{tikzpicture}%}}}
  \caption{$\alpha_i$: $C^j \to S^{j-1,0}$}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (C) -- node[below] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (tlll-1) -- (W-20) node[above] {$i$}
      (xor-1) -- (txor-1) (txor-1) -- (W-21) node[above] {$i$}
      (xnd-1) -- (and-1)
      (W40) node[below] {\phantom{$i$}}
      ;
  \end{tikzpicture}%}}}
  \caption{$\beta_i$: $C^j \to S^{j,0}, S^{j,1}$}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (W-21) node[above] {$i$} -- (xnd1) (xnd1) -- (xor1) (xor1) -- (lll1)
      (xnd1) -- (and1)
      (xor1) -- (txor1)
      (txor1) -- (W-24) node[above] {$i$}
      (lll1) -- (W41) node[below] {$i-1$}
      ;
  \end{tikzpicture}%}}}
  \caption{$\gamma_i$: $S^{j,1}, S^{j,4} \to S^{j+1,1}$}
  \end{subfigure}
  \caption{\cipher{MiniMorus} linear approximation fragments.}
  \label{fig:minimorus}
\end{figure}
\end{document}

>>>>

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{subfigure}{.3\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (C) -- node[below] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (xnd-1) -- (and-1) (xor-1) -- (txor-1) (txor-1) -- (tanB0) (tanB0) -- (tanB0-|and0.east)
      (and0) -- (xnd0) (xnd0) -- (tlll-1) (xnd0) -- (xor0)
      (and-1.east|-tanA-1) -- (tanA-1) (tanA-1) -- (txor0) (txor0) -- (xor0)
      (xor0) -- (lll0) (lll0) -- (W40) node[below] {$i+5$}
      (W-20) node[above] {\phantom{$i$}}
      ;
  \end{tikzpicture}%}}}
  \caption{$\alpha_i$: $C^j \to S^{j-1,0}$}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\textwidth}
  \centering
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (C) -- node[below] {$i$} (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (tlll-1) -- (W-20) node[above] {$i$}
      (xor-1) -- (txor-1) (txor-1) -- (W-21) node[above] {$i$}
      (xnd-1) -- (and-1)
      (W40) node[below] {\phantom{$i$}}
      ;
  \end{tikzpicture}%}}}
  \caption{$\beta_i$: $C^j \to S^{j,0}, S^{j,1}$}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (W-21) node[above] {$i$} -- (xnd1) (xnd1) -- (xor1) (xor1) -- (lll1)
      (xnd1) -- (and1)
      (xor1) -- (txor1)
      (txor1) -- (W-24) node[above] {$i$}
      (lll1) -- (W41) node[below] {$i-1$}
      ;
  \end{tikzpicture}%}}}
  \caption{$\gamma_i$: $S^{j,1}, S^{j,4} \to S^{j+1,1}$}
  \end{subfigure}
  \bigskip

  \begin{subfigure}{.3\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (W-24) node[above] {$i$} -- (xnd4) (xnd4) -- (xor4) (xnd4) -- (and4)
      (xor4) -- (lll4) (xor4) -- (txor4) (txor4) -- (W42) node[below] {$i$}
      (lll4) -- (W44) node[below] {$i+13$}
      ;
  \end{tikzpicture}%}}}
  \caption{$\delta_i$: $S^{j,4} \to S^{j+1,2}, S^{j+1,4}$}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\textwidth}
  \begin{tikzpicture}[xscale=0.75,yscale=1.5]%{{{
    \printstate
    \draw[trail]
      (W-22) node[above] {$i$} -- (xnd2) (xnd2) -- (xor2) (xnd2) -- (and2)
      (xor2) -- (lll2) (xor2) -- (txor2) (txor2) -- (W40) node[below] {$i$}
      (lll2) -- (W42) node[below] {$i+7$}
      ;
  \end{tikzpicture}%}}}
  \caption{$\varepsilon_i$: $S^{j,2} \to S^{j+1,0}, S^{j+1,2}$}
  \end{subfigure}
  \caption{\cipher{MiniMorus} linear approximation fragments.}
  \label{fig:minimorus}
\end{figure}
\end{document}
